---
title: "Class 6"
author: "Gloria Zhang"
date: "January 24, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Section 1: Reading files again :-)

Here we are going to try using the **read.table()** function and friends to read some example flat files.

First lets try adding a simple plot. Write any R code by inserting an R code block
```{r}
plot(1:10)
```

Read some data but inserting R code using the shortcut: "option + command + i""
One way is to download the file. Can also just put in the link.
```{r}
test=read.table("test1.txt", header=TRUE, sep=",")
test

```
```{r}
read.table( "https://bioboot.github.io/bimm143_W19/class-material/test1.txt", header= TRUE, sep= ",")
```

For this common CSV format we can use **read.csv()**
Another way to read links.
```{r}
file1 <- "https://bioboot.github.io/bimm143_W19/class-material/test1.txt"
read.csv(file1)
```

```{r}
file2 <- "https://bioboot.github.io/bimm143_W19/class-material/test2.txt"
read.csv(file2,sep = "$", header= TRUE)
```

```{r}
file3 <- "https://bioboot.github.io/bimm143_W19/class-material/test3.txt"
read.table(file3)
```
 
 
### Section 2

My first silly function
```{r}
add <- function(x, y=1){
  #Sum the input x and y
  x+y
}

```

Let's try using this function

```{r}
add(1) 
```

```{r}
add(1,100)
```


```{r}
add(c(1,2,3))
```

```{r}
add(c(1,2,3),4)
```

Only two variables are defined.
```{r}
#add(1,2,2)

```

Can't add letters
```{r}
#add(x=1, y="b")
```

My 2nd function

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

Test on a small example where we know what the answer should be!
```{r}
rescale(1:10)
```

```{r}
# How would you get your function to work here?
rescale(c(1,2,NA,3,10))
```

```{r}
# What should your function do here?
rescale(c(1,10,"string"))
```

```{r}
rescale2 <- function(x) {
  rng <- range(x,na.rm=TRUE)
  (x-rng[1]/(rng[2]-rng[1]))
}
x <- c(1,2,NA,3,10)
rng <- range(x)
#rng
```

```{r}
rescale2(c(1,2,NA,3,10))
```

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 rng <-range(x, na.rm=na.rm)
 print("Hello")
 answer <- (x - rng[1]) / (rng[2] - rng[1])
 print("is it me you are looking for?")
 if(plot) {
 plot(answer, typ="b", lwd=4)
   print("please do not ever sing again")
 }
 print("I can see it in ...")
 return(answer)
}
```

```{r}
rescale3(c(1:6,NA,10), plot=TRUE)
```

## Working with the bio3d package

To install this package, use **install.packages("bio3d")**

```{r}
library(bio3d)
```

```{r}
# Read a PDB file from the the database
s1 <- read.pdb("4AKE") # kinase with drug
s1
```

```{r}
# Can you improve this analysis code?
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")
s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```




